(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-09 table_fpp.tex
ok, bold really working?
put back red for FPs

\begin{deluxetable*}{lccccccc}

@@

\colhead{FPP}

@@

 {\bf $201208431$ } & {\bf  $1$ } & {\bf  $0.51$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0058$ } & {\bf  $0.00011$ } & {\bf  $0.22$ } & {\bf  $0.0059$} \\
 \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.072$  & \color{red}  $0.93$  & \color{red}  $0.22$  & \color{red}  $1$\\
 {\bf $201295312$ } & {\bf  $1$ } & {\bf  $0.04$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.008$ } & {\bf  $0.00014$ } & {\bf  $0.15$ } & {\bf  $0.0082$} \\
$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ \\
 {\bf $201338508$ } & {\bf  $2$ } & {\bf  $0.33$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.17$ } & {\bf  $0.006$} \\
 {\bf $201367065$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.01$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.18$ } & {\bf  $0.01$} \\
 {\bf $201367065$ } & {\bf  $2$ } & {\bf  $0.67$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00063$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.14$ } & {\bf  $0.00063$} \\
 {\bf $201384232$ } & {\bf  $1$ } & {\bf  $0.44$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00017$ } & {\bf  $0.00023$ } & {\bf  $0.21$ } & {\bf  $0.0004$} \\
$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ \\
 {\bf $201403446$ } & {\bf  $1$ } & {\bf  $0.18$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0069$ } & {\bf  $0.0013$ } & {\bf  $0.13$ } & {\bf  $0.0083$} \\
$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ \\
$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ \\
$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ \\
 \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.13$  & \color{red}  $0.86$  & \color{red}  $0.18$  & \color{red}  $0.99$\\
 {\bf $201505350$ } & {\bf  $2$ } & {\bf  $0.70$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0025$ } & {\bf  $0.00013$ } & {\bf  $0.07$ } & {\bf  $0.0026$} \\
 {\bf $201546283$ } & {\bf  $1$ } & {\bf  $0.15$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.16$ } & {\bf  $< 10^{-4}$} \\
$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ \\
 {\bf $201555883$ } & {\bf  $1$ } & {\bf  $0.94$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0044$ } & {\bf  $0.0004$ } & {\bf  $0.20$ } & {\bf  $0.0048$} \\
 \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0023$  & \color{red}  $0.14$  & \color{red}  $0.82$  & \color{red}  $0.07$  & \color{red}  $0.96$\\
$201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ \\
 {\bf $201577035$ } & {\bf  $1$ } & {\bf  $0.14$ } & {\bf  $< 10^{-4}$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00015$ } & {\bf  $0.20$ } & {\bf  $0.0002$} \\
$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ \\
 {\bf $201613023$ } & {\bf  $1$ } & {\bf  $0.08$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0016$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.15$ } & {\bf  $0.0016$} \\
$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ \\
 {\bf $201629650$ } & {\bf  $1$ } & {\bf  $0.43$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.005$ } & {\bf  $0.0012$ } & {\bf  $0.17$ } & {\bf  $0.0062$} \\
$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ \\
 \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}  $0.81$  & \color{red}  $0.0016$  & \color{red}  $0.13$  & \color{red}  $0.01$  & \color{red}  $0.94$\\
$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ \\
 {\bf $201736247$ } & {\bf  $1$ } & {\bf  $0.42$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0015$ } & {\bf  $0.00092$ } & {\bf  $0.22$ } & {\bf  $0.0024$} \\
$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ \\
$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ \\
$201779067$ & $1$ & $1.97$ & $0.034$ & $0.038$ & $0.3$ & $0.03$ & $0.37$ \\
$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ \\
 {\bf $201855371$ } & {\bf  $1$ } & {\bf  $0.62$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.0006$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.20$ } & {\bf  $0.00071$} \\
 {\bf $201912552$ } & {\bf  $1$ } & {\bf  $0.47$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.00058$ } & {\bf  $< 10^{-4}$ } & {\bf  $0.22$ } & {\bf  $0.00058$} \\
$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$

>>>>

\begin{deluxetable*}{lcllllllc}

@@

\colhead{FPP} &
\colhead{Disposition}

@@

$201208431$ & $1$ & $0.51$ & $< 10^{-4}$ & $0.0058$ & $0.00011$ & $0.22$ & $0.0059$ & Validated \\
 \color{red} $201257461$  & \color{red}  $1$  & \color{red}  $0.59$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.072$  & \color{red}  $0.93$  & \color{red}  $0.22$  & \color{red}  $1$  & \color{red}  FP\\
$201295312$ & $1$ & $0.04$ & $< 10^{-4}$ & $0.008$ & $0.00014$ & $0.15$ & $0.0082$ & Validated \\
$201338508$ & $1$ & $0.63$ & $< 10^{-4}$ & $0.031$ & $0.00063$ & $0.17$ & $0.032$ & Candidate \\
$201338508$ & $2$ & $0.33$ & $< 10^{-4}$ & $0.006$ & $< 10^{-4}$ & $0.17$ & $0.006$ & Validated \\
$201367065$ & $1$ & $0.15$ & $< 10^{-4}$ & $0.01$ & $< 10^{-4}$ & $0.18$ & $0.01$ & Validated \\
$201367065$ & $2$ & $0.67$ & $< 10^{-4}$ & $0.00063$ & $< 10^{-4}$ & $0.14$ & $0.00063$ & Validated \\
$201384232$ & $1$ & $0.44$ & $< 10^{-4}$ & $0.00017$ & $0.00023$ & $0.21$ & $0.0004$ & Validated \\
$201393098$ & $1$ & $0.52$ & $< 10^{-4}$ & $0.02$ & $0.024$ & $0.17$ & $0.044$ & Candidate \\
$201403446$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.0069$ & $0.0013$ & $0.13$ & $0.0083$ & Validated \\
$201445392$ & $1$ & $0.26$ & $< 10^{-4}$ & $0.013$ & $0.053$ & $0.22$ & $0.067$ & Candidate \\
$201445392$ & $2$ & $0.18$ & $< 10^{-4}$ & $0.22$ & $0.048$ & $0.18$ & $0.27$ & Candidate \\
$201465501$ & $1$ & $0.68$ & $< 10^{-4}$ & $0.15$ & $0.0028$ & $0.14$ & $0.15$ & Candidate \\
 \color{red} $201505350$  & \color{red}  $1$  & \color{red}  $2.69$  & \color{red}  $< 10^{-4}$  & \color{red}  $0.13$  & \color{red}  $0.86$  & \color{red}  $0.18$  & \color{red}  $0.99$  & \color{red}  FP\\
$201505350$ & $2$ & $0.70$ & $< 10^{-4}$ & $0.0025$ & $0.00013$ & $0.07$ & $0.0026$ & Validated \\
$201546283$ & $1$ & $0.15$ & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.16$ & $< 10^{-4}$ & Validated \\
$201549860$ & $1$ & $0.18$ & $< 10^{-4}$ & $0.013$ & $0.00071$ & $0.20$ & $0.014$ & Candidate \\
$201555883$ & $1$ & $0.94$ & $< 10^{-4}$ & $0.0044$ & $0.0004$ & $0.20$ & $0.0048$ & Validated \\
 \color{red} $201565013$  & \color{red}  $1$  & \color{red}  $1.69$  & \color{red}  $0.0023$  & \color{red}  $0.14$  & \color{red}  $0.82$  & \color{red}  $0.07$  & \color{red}  $0.96$  & \color{red}  FP\\
$201569483$ & $1$ & $2.06$ & $0.48$ & $0.00061$ & $0.097$ & $0.01$ & $0.58$ & Candidate \\
$201577035$ & $1$ & $0.14$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.00015$ & $0.20$ & $0.0002$ & Validated \\
$201596316$ & $1$ & $0.45$ & $< 10^{-4}$ & $0.01$ & $0.0023$ & $0.17$ & $0.013$ & Candidate \\
$201613023$ & $1$ & $0.08$ & $< 10^{-4}$ & $0.0016$ & $< 10^{-4}$ & $0.15$ & $0.0016$ & Validated \\
$201617985$ & $1$ & $0.27$ & $< 10^{-4}$ & $0.12$ & $0.0017$ & $0.16$ & $0.12$ & Candidate \\
$201629650$ & $1$ & $0.43$ & $< 10^{-4}$ & $0.005$ & $0.0012$ & $0.17$ & $0.0062$ & Validated \\
$201635569$ & $1$ & $0.79$ & $< 10^{-4}$ & $0.052$ & $0.071$ & $0.09$ & $0.12$ & Candidate \\
 \color{red} $201649426$  & \color{red}  $1$  & \color{red}  $3.10$  & \color{red}  $0.81$  & \color{red}  $0.0016$  & \color{red}  $0.13$  & \color{red}  $0.01$  & \color{red}  $0.94$  & \color{red}  FP\\
$201702477$ & $1$ & $0.70$ & $< 10^{-4}$ & $0.03$ & $0.29$ & $0.06$ & $0.32$ & Candidate \\
$201736247$ & $1$ & $0.42$ & $< 10^{-4}$ & $0.0015$ & $0.00092$ & $0.22$ & $0.0024$ & Validated \\
$201754305$ & $1$ & $0.65$ & $< 10^{-4}$ & $0.015$ & $0.0016$ & $0.18$ & $0.017$ & Candidate \\
$201754305$ & $2$ & $0.38$ & $< 10^{-4}$ & $0.0099$ & $0.00069$ & $0.17$ & $0.011$ & Candidate \\
$201779067$ & $1$ & $1.97$ & $0.034$ & $0.038$ & $0.3$ & $0.03$ & $0.37$ & Candidate \\
$201828749$ & $1$ & $0.39$ & $< 10^{-4}$ & $0.014$ & $0.0024$ & $0.17$ & $0.016$ & Candidate \\
$201855371$ & $1$ & $0.62$ & $< 10^{-4}$ & $0.0006$ & $< 10^{-4}$ & $0.20$ & $0.00071$ & Validated \\
$201912552$ & $1$ & $0.47$ & $< 10^{-4}$ & $0.00058$ & $< 10^{-4}$ & $0.22$ & $0.00058$ & Validated \\
$201929294$ & $1$ & $3.12$ & $< 10^{-4}$ & $0.053$ & $0.055$ & $0.05$ & $0.11$ & Candidate
